A data-driven, pixel-level model to improve the precision of \Kepler\ photometry

### 2013-10-23 documents/plm.tex
language tweaks -- solving not optimizing

The train-and-test idea comes into the objective function $\chi^2_{mn}$:
When we are computing the objective function $\chi^2_{mn}$,
  we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
We train the model---that is, set the parameters $a_{mnm'}$ and $b_{mnk}$---%
  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
Importantly, and perhaps surprisingly, this is a \emph{different objective function}
  for every target data point (pixel value to be predicted) $I_{mn}$,
  and we have to do a \emph{independent optimization} of the parameters for every pixel value we want to predict.
That is, every pixel datum $I_{mn}$ we predict will have
  \emph{different} settings of the parameters $a_{mnm'}$ and $b_{mnk}$.
Since there are about $10^{11}$ total pixel values in the \Kepler\ Target Pixel Files,
  this represents one fuck of a lot of optimizations,
  and a lot of parameters to obtain and record.

For this reason---\emph{so many optimizations}---%
  we do \todo{some crazy clever stuff} to make this work fast;
  \todo{DFM implementation notes here}.

>>>>

The train-and-test idea comes into the objective function $\chi^2_{mn}$:
When we are computing the objective function $\chi^2_{mn}$,
  we are using only time points $n'\in\set{N}_n$ that don't overlap the target (or test) time point $n$.
We train the model---that is, set the parameters $a_{mnm'}$ and $b_{mnk}$---%
  by choosing the full set of parameters that jointly minimize the objective function $\chi^2_{mn}$.
Fortunately, given the form of the model,
  this minimization is just a linear solve (linear operation on the data).
Importantly however, and perhaps surprisingly, the objective function $\chi^2_{mn}$ is \emph{different}
  for every target data point (pixel value to be predicted) $I_{mn}$;
  we have to do an \emph{independent optimization} (or really linear solve)
  of the parameters for every pixel value we want to predict.
That is, every pixel datum $I_{mn}$ we predict will have
  \emph{different} settings of the parameters $a_{mnm'}$ and $b_{mnk}$.
Since there are of order $10^{6}$ total pixel values in the \Kepler\ Target Pixel Files for \emph{each \Kepler\ target},
  and of order $10^7$ data sources used as basis functions in the linear fitting,
  this represents one fuck of a lot of linear solves,
  and a lot of parameters to obtain and record.

For this reason---\emph{so many solves}---%
  we do \todo{some crazy clever stuff} to make this work fast;
  \todo{DFM implementation notes here}.
